Proof-Pattern Search in Coq/SSReflect

### 2015-02-04 ACMTransCL/visualisation.tex
Remove commented-out parts

$$
\xy0;/r.12pc/: 
*[o]=<80pt,30pt>\hbox{\txt{Coq libraries:\\one or many?}}="a"*\frm<8pt>{-,},
(40,35)*[o]=<80pt,30pt>\hbox{\txt{General\\pattern-search}}="r"*\frm<8pt>{-},
(40,-35)*[o]=<80pt,30pt>\hbox{\txt{Relative to\\ Coq object}}="b"*\frm<8pt>{-},
(80,55)*[o]=<80pt,15pt>\hbox{\txt{Terms}}="c"*\frm<8pt>{-},
(80,15)*[o]=<80pt,15pt>\hbox{\txt{Proofs}}="d"*\frm<8pt>{-},
(80,-15)*[o]=<80pt,15pt>\hbox{\txt{Terms}}="e"*\frm<8pt>{-},
(80,-55)*[o]=<80pt,15pt>\hbox{\txt{Proofs}}="f"*\frm<8pt>{-},
(160,55)*[o]=<120pt,15pt>\hbox{\txt{Visualise term clusters?}}="g"*\frm<8pt>{-,},
(160,15)*[o]=<120pt,15pt>\hbox{\txt{Visualise proof families?}}="h"*\frm<8pt>{-,},
(160,-15)*[o]=<120pt,15pt>\hbox{\txt{Visualise the term tree?}}="i"*\frm<8pt>{-,},
(160,-55)*[o]=<120pt,15pt>\hbox{\txt{Visualise the proof flow?}}="j"*\frm<8pt>{-,},
"a";"b" **\dir{-} ?>*\dir{>},
"a";"r" **\dir{-} ?>*\dir{>},
"r";"c" **\dir{-} ?>*\dir{>},
"r";"d" **\dir{-} ?>*\dir{>},
"b";"e" **\dir{-} ?>*\dir{>},
"b";"f" **\dir{-} ?>*\dir{>},
"c";"g" **\dir{-} ?>*\dir{>},
"d";"h" **\dir{-} ?>*\dir{>},
"e";"i" **\dir{-} ?>*\dir{>},
"f";"j" **\dir{-} ?>*\dir{>},
%"r";"a" **\dir{-} ?>*\dir{>},
%"c";"d" **\dir{-} ?>*\dir{>},
%"d";"h" **\dir{-} ?>*\dir{>},
%"c";"e" **\dir{-} ?>*\dir{>},
%"e";"c" **\dir{-} ?>*\dir{>}
%+<0em,0em>@+ 
\endxy
$$
\caption{Visualisation techniques included in ML4PG.}\label{fig:visualisation}
\end{figure}

In the previous sections, we have seen how ML4PG can be used to find families of proofs following 
a common pattern, and use those families to automatically prove theorems. However, when the proof-generation
method fails, the output provided by ML4PG algorithms is just a set of similar patches with no hints of why 
these proof-patches are deemed similar. 
% In addition, the user needs
% to replay the proof to infer the pattern. %Therefore, the conceptualisation of proof-patterns can be
% %a challenge. 
In this section, we present our approach to facilitate the understanding of proof patterns using different visualisation tools
that are summarised in Figure~\ref{fig:visualisation}.

@@

ML4PG uses this information and produces an automaton-shape representation for discovered % to help in the visualisation of 
proof-patterns and the correlated features that determined the patterns. In our example, the associated ``automaton'' is depicted in Figure~\ref{fig:automata}. 
\end{example}

% This feature selection mechanism helps to explain why the proof-patches are similar since it indicates the 
% features that have been relevant for the construction of the cluster. To show the selected features and their relation with 
% the proof-patches, we introduce an automaton-shape representation. In~\cite{GWR14}, a tool to infer models 
% from proof traces was presented. Those models help to understand the behaviour exhibited by a collection
% of proofs and is represented by automata.

@@

\begin{figure}[t]
\centering 
\includegraphics[scale=.19]{itp6.png}
\caption{\scriptsize{\emph{Fragment of the automaton 
 corresponding to the cluster of four lemma fragments described in the case study of Section~\ref{sec:recurrent}} (the whole automaton can be seen in Appendix~\ref{sec:automaton}). 
It shows correspondence between certain proof steps of lemmas % the following lemmas were discovered:
\texttt{telescope} (for the lemma of Example~\ref{example0}), \texttt{nilpotent\_inverse} (for Lemma~\ref{lem:nilpotent2}), and \texttt{persistent\_homology} 
(for Lemma~\ref{lem:fundamental}). Square boxes denote feature correlation where it exists. 
To be compact, we  hide full lemma statements, tactic and auxiliary lemma names, symbols, etc., but they can be shown by ML4PG. 
%For example, the full statements of the following cluster lemmas will be shown:
%The names of the lemmas of that cluster are: 
}}\label{fig:automata}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=.3]{clustervisualisation.png}
\caption{Cluster visualisation for the case study included at the end of Section~\ref{sec:recurrent} regarding the families of similar lemmas to Lemma~\ref{lem:nilpotent}: \texttt{telescope} (for the lemma of Example~\ref{example0}), \texttt{nilpotent\_inverse} (for Lemma~\ref{lem:nilpotent2}), and \texttt{persistent\_homology} 
(for Lemma~\ref{lem:fundamental}). The outer, middle and inner square contain, respectively, the proof-patches obtained with granularities 1, 3 and 5. It shows correspondence between certain proof steps of lemmas % the following lemmas were discovered:
}\label{fig:clustervisualisation} 
\end{figure}

%for clustering that are related to that 
%state.

% $-$ there are several transitions from the $j$th to the $j+1$th state labelled by the $j$th tactic of each proof-patch of $P$ -- if either the $j$th tactic of two or more
% proof-patches is the same or belong to the same group (see Table~\ref{tab:tactics}), the transitions are merged in a unique transition labelled with the set of those tactics,
% 
% $-$ if a proof ends after the $j$th tactic of a proof-patch, the $j+1$ state is represented as final.

%\begin{example}

%\end{example}

>>>>

$$
\xy0;/r.12pc/:
*[o]=<80pt,30pt>\hbox{\txt{Coq libraries:\\one or many?}}="a"*\frm<8pt>{-,},
(40,35)*[o]=<80pt,30pt>\hbox{\txt{General\\pattern-search}}="r"*\frm<8pt>{-},
(40,-35)*[o]=<80pt,30pt>\hbox{\txt{Relative to\\ Coq object}}="b"*\frm<8pt>{-},
(80,55)*[o]=<80pt,15pt>\hbox{\txt{Terms}}="c"*\frm<8pt>{-},
(80,15)*[o]=<80pt,15pt>\hbox{\txt{Proofs}}="d"*\frm<8pt>{-},
(80,-15)*[o]=<80pt,15pt>\hbox{\txt{Terms}}="e"*\frm<8pt>{-},
(80,-55)*[o]=<80pt,15pt>\hbox{\txt{Proofs}}="f"*\frm<8pt>{-},
(160,55)*[o]=<120pt,15pt>\hbox{\txt{Visualise term clusters?}}="g"*\frm<8pt>{-,},
(160,15)*[o]=<120pt,15pt>\hbox{\txt{Visualise proof families?}}="h"*\frm<8pt>{-,},
(160,-15)*[o]=<120pt,15pt>\hbox{\txt{Visualise the term tree?}}="i"*\frm<8pt>{-,},
(160,-55)*[o]=<120pt,15pt>\hbox{\txt{Visualise the proof flow?}}="j"*\frm<8pt>{-,},
"a";"b" **\dir{-} ?>*\dir{>},
"a";"r" **\dir{-} ?>*\dir{>},
"r";"c" **\dir{-} ?>*\dir{>},
"r";"d" **\dir{-} ?>*\dir{>},
"b";"e" **\dir{-} ?>*\dir{>},
"b";"f" **\dir{-} ?>*\dir{>},
"c";"g" **\dir{-} ?>*\dir{>},
"d";"h" **\dir{-} ?>*\dir{>},
"e";"i" **\dir{-} ?>*\dir{>},
"f";"j" **\dir{-} ?>*\dir{>},
\endxy
$$
\caption{Visualisation techniques included in ML4PG.}\label{fig:visualisation}
\end{figure}

In the previous sections, we have seen how ML4PG can be used to find families of proofs following
a common pattern, and use those families to automatically prove theorems. However, when the proof-generation
method fails, the output provided by ML4PG algorithms is just a set of similar patches with no hints of why
these proof-patches are deemed similar.
In this section, we present our approach to facilitate the understanding of proof patterns using different visualisation tools
that are summarised in Figure~\ref{fig:visualisation}.

@@

ML4PG uses this information and produces an automaton-shape representation for discovered
proof-patterns and the correlated features that determined the patterns. In our example, the associated ``automaton'' is depicted in Figure~\ref{fig:automata}.
\end{example}

@@

\begin{figure}[t]
\centering
\includegraphics[scale=.19]{itp6.png}
\caption{\scriptsize{\emph{Fragment of the automaton
 corresponding to the cluster of four lemma fragments described in the case study of Section~\ref{sec:recurrent}} (the whole automaton can be seen in Appendix~\ref{sec:automaton}).
It shows correspondence between certain proof steps of lemmas
\texttt{telescope} (for the lemma of Example~\ref{example0}), \texttt{nilpotent\_inverse} (for Lemma~\ref{lem:nilpotent2}), and \texttt{persistent\_homology}
(for Lemma~\ref{lem:fundamental}). Square boxes denote feature correlation where it exists.
To be compact, we  hide full lemma statements, tactic and auxiliary lemma names, symbols, etc., but they can be shown by ML4PG.
}}\label{fig:automata}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=.3]{clustervisualisation.png}
\caption{Cluster visualisation for the case study included at the end of Section~\ref{sec:recurrent} regarding the families of similar lemmas to Lemma~\ref{lem:nilpotent}: \texttt{telescope} (for the lemma of Example~\ref{example0}), \texttt{nilpotent\_inverse} (for Lemma~\ref{lem:nilpotent2}), and \texttt{persistent\_homology}
(for Lemma~\ref{lem:fundamental}). The outer, middle and inner square contain, respectively, the proof-patches obtained with granularities 1, 3 and 5. It shows correspondence between certain proof steps of lemmas
}\label{fig:clustervisualisation}
\end{figure}
